---
title: "Project 4"
author: "<center><b>Carson Youman, Ryan Allen Mangin, Seongwoo Jeong, & Stefanos Kapetanakis</b></center>"
output:
  html_document:
    toc: yes
  html_notebook:
    toc: yes
---

```{r sessionInfo}
sessionInfo(package=NULL)
```

#**Cleaning the Data**
We cleaned our data using the R script we created named AustinHousingETL.R in the 01 Data folder. This script creates a csv file named Austin_Housing_Data.csv. We then uploaded this cleaned data to data.world. 

```{r source, include=FALSE}
source("../01 Data/AustinHousingETL.R")
```
#**Getting the Data**
The data for this project can be found and accessed at https://data.world/stefkaps/s-17-edv-project-4 assuming proper permissions. If you do not have permission but wish to gain it, message the user at the following URL: https://data.world/stefkaps

#**2014 Housing Market Analysis**
We downloaded the 2014 Housing Market Data for the City of Austin from the data.gov website. This data is broken down by zip code and lists a variety of statistics associated with the zip code. Using this data, we created three visualizations of the data showing the following relationships:<br /><br />
<ol>
<li></li>
<li></li>
<li></li>

</ol>